Palaeobiology demo: disparity-through-time and within groups

### 2020-11-10 inst/gitbook/08_palaeo-demo.Rmd
fixed typo in the paleo demo

## Plotting the bootstrapped and rarefied results
plot(disparity, type = "continuous", main = "bootstrapped results")
plot(disparity, type = "continuous", main = "rarefied results",
     rarefaciton = minimum_size)
```

>>>>

## Plotting the bootstrapped and rarefied results
plot(disparity, type = "continuous", main = "bootstrapped results")
plot(disparity, type = "continuous", main = "rarefied results",
     rarefaction = minimum_size)
```
